CRUSE to Safe Cycling in Ireland

### 2023-09-12 cruse-paper.qmd
Update bibliography and intro

[@lovelace2017]

• Title page/main information (title, full names and institutional addresses for all
authors, indication of the corresponding author)
• Abstract
• Introduction

@@

## Availability of data and material {.unnumbered}
## Funding {.unnumbered}
## Acknowledgements {.unnumbered}
## Competing interests {.unnumbered}
## Authors' contributions {.unnumbered}

>>>>

Transport is a major contributor to climate change, premature death due to road traffic collisions and air pollution, yet has the potential to be a major contributor to decarbonization and improved public health.
Transport is responsible for 23% of global emissions, 70% of which is from road transport, nearly half of which is from passenger cars [@jaramillo2022].
The transport system encourages, enables and in some cases enforces unsustainable lifestyles, including over-consumption of goods due to excessive mobile storage space and dependency on services that are only accessible by car due to land use plans that have built up around roads [@gray2001; @shergold2012; @motte-baumvol2010].

@@

## Availability of data and material {.unnumbered}

## Funding {.unnumbered}

## Acknowledgements {.unnumbered}

## Competing interests {.unnumbered}

## Authors' contributions {.unnumbered}
